diffusion, websites with 1 pc

### 2022-05-30 src/level_lisa_la.Rmd
edits

@@

path.out <- paste0(path,"/outputs/rsq_dist_london_la.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_london_la.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_city_la.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city_la.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_centre_la.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre_la.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

>>>>

# No need to add 0s like OAs as there aren't any LA with 0s

@@

path.out <- paste0(path,"/outputs/rsq_dist_london_la.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_london_la.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_city_la.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city_la.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_centre_la.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre_la.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, LA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

### 2022-05-30 src/level_lisa_oa.Rmd
edits

```{r}
path.out <- paste0(path, "/outputs/morani.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  kable() #%>% 
  #write_csv(path.out)

@@

@@

for (t in 1996:2012){
    a <- df %>% filter(year==t)
  b <- as.data.frame(gini(a$n))
  b$year = t
  gini.df <- rbind(gini.df, b)
}

path.out <- paste0(path, "/outputs/gini.csv")
gini.df %>% write_csv(path.out)
```

@@

# NOT USED AS IT SCREWS UP THE REGRESSIONS
# Complete panel, N = 3871903, 17 year * 227759 OA
# df <- df %>% bind_rows(dist %>% select(oa11cd)) %>% 
#   mutate(year = ifelse(is.na(year),1000, year),
#          country = substring(oa11cd, 1, 1)) %>% 
#   filter(country != "L" & country != "M" & country != "N") %>% 
#   filter(!is.na(country)) %>% 
#   complete(year, oa11cd, fill = list(n = 0)) %>% 
#   filter(year!=1000,
#          !is.na(oa11cd)) %>% 
#   select(-country)

@@

@@

path.out <- paste0(path,"/outputs/rsq_dist_london.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_london.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_city.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_centre.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

# library(pscl)
# m1 <- zeroinfl((n) ~ log(dist.retail+0.001),
#   data = df[df$year==t,], dist = "negbin", EM = TRUE)
# summary(m1)
# 
# df %>% filter(year == 1996) %>% 
#   group_by(group = cut(n, breaks = c(0, 1, 2, 10, 100, 1000, 10000), include.lowest = T, right = F)) %>%  #seq(0, max(n), 100))) %>%
#   summarise(n = sum(n))
```

>>>>

```{r}
path.out <- paste0(path, "/outputs/morani_oa.csv")
morani %>% as_tibble() %>% 
  rename('morani'=V1,
                   p = V2,
                   year = V3) %>% 
  kable() #%>% 
  #write_csv(path.out)

@@

# add OAs with 0s
df.with0s <- df %>% mutate(country = substring(oa11cd, 1, 1)) %>%
  filter(country != "L" & country != "M" & country != "N") %>%
  filter(!is.na(country)) %>%
  complete(year, oa11cd, fill = list(n = 0)) %>%
  filter(year!=1000,
         !is.na(oa11cd)) %>%
  dplyr::select(-country)

@@

for (t in 1996:2012){
    a <- df.with0s %>% filter(year==t)
  b <- as.data.frame(gini(a$n))
  b$year = t
  gini.df <- rbind(gini.df, b)
}

path.out <- paste0(path, "/outputs/gini_oa.csv")
gini.df %>% write_csv(path.out)
```

@@

# NOT USED AS IT SCREWS UP THE REGRESSIONS
# Complete panel, N = 3871903, 17 year * 227759 OA
# df <- df %>% bind_rows(dist %>% dplyr::select(oa11cd)) %>%
#   mutate(year = ifelse(is.na(year),1000, year),
#          country = substring(oa11cd, 1, 1)) %>%
#   filter(country != "L" & country != "M" & country != "N") %>%
#   filter(!is.na(country)) %>%
#   complete(year, oa11cd, fill = list(n = 0)) %>%
#   filter(year!=1000,
#          !is.na(oa11cd)) %>%
#   dplyr::select(-country)

@@

# calculate area
oa.gb$area <- area(oa.gb) #/ 1000000

@@

path.out <- paste0(path,"/outputs/rsq_dist_london_oa.png")
ggplot(dens.London) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_london_oa.png")
ggplot(out.model, aes(x=reorder(year, year), y=estimate)) +
#ggplot(out.model, aes(x=year, y = estimate)) +  
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to London on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

r2.all <- dens.London %>% 
  rename(London = rsquared)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_city_oa.png")
ggplot(dens.distMet) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_city_oa.png")
ggplot(out.modelMet, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

r2.all <- r2.all %>% left_join(dens.distMet) %>% 
  rename(cities = rsquared)
```

@@

path.out <- paste0(path,"/outputs/rsq_dist_centre_oa.png")
ggplot(dens.dist.retail) +
  geom_line(aes(x=year, y = rsquared)) +
  ylab("Rsquared") + 
  ggtitle("Regression fit, distance to nearest retail centre on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

@@

path.out <- paste0(path,"/outputs/b_dist_centre_oa.png")
ggplot(out.model.retail, aes(x=reorder(year, year), y=estimate)) +
           geom_errorbar(aes(ymin=conf.low, ymax=conf.high), 
                       width = 0.2,size  = 1,
                       position = "dodge", color="turquoise4") +
  #geom_hline(yintercept = 0, color = "red", size = 1) +
  geom_point() + coord_flip() +
  ylab("distance coefficient") + xlab("") + 
  ggtitle("Regression coefficients, distance to nearest city on website density, OA") +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggsave(path.out)

# library(pscl)
# m1 <- zeroinfl((n) ~ log(dist.retail+0.001),
#   data = df[df$year==t,], dist = "negbin", EM = TRUE)
# summary(m1)
# 
# df %>% filter(year == 1996) %>% 
#   group_by(group = cut(n, breaks = c(0, 1, 2, 10, 100, 1000, 10000), include.lowest = T, right = F)) %>%  #seq(0, max(n), 100))) %>%
#   summarise(n = sum(n))
```
All R^2 dataframe

```{r}
path.out <- paste0(path, "/outputs/r2_all.csv")

r2.all <- dens.London %>% 
  rename(London = rsquared) %>% 
  left_join(dens.distMet) %>% 
  rename(cities = rsquared) %>% 
  left_join(dens.dist.retail) %>% 
  rename(retail = rsquared) %>% 
  relocate(year, .before = London) %>% 
  arrange(year)

write_csv(r2.all, path.out)
```
